Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities

### 2015-04-17 Paper2015.tex
working process

Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2014}.
The analytical model therefore exceeds the present calculations about TBD\%.
\todo{Complete quantification at CUP}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP and SUP}

@@

\bibitem{tbd0} \todo{Add referencefor Geant4}

\bibitem{tbd1} \todo{Complete reference for \U238}

\bibitem{tbd2} \todo{Complete reference for dose conversion}

>>>>

Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from an analytical model~\cite{Prokofiev2014}.
The analytical model therefore exceeds the present calculations about 49\%.
\todo{Complete quantification at CUP}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP and SUP}

@@

\bibitem{Truscott2006} 
Truscott, P. et al.,
\newblock Neutron Energy-Deposition Spectra Measurements, and Comparisons with Geant4 Predictions
\newblock{\em Proc. IEEE Trans. Nucl. Sci. 2006} pp 1883-1889

\bibitem{Carlson2009}
Carlson, A. D. et al.,
\newblock International Evaluation of Neutron Cross Section Standards
\newblock{\em Proc. Nucl. Data Sheets 2009} pp 3215-3324

\bibitem{Kwon1980} 
Kwon, S.-G. et al.,
\newblock Calculation of Neutron and Gamma-Ray Flux-to-Dose-Rate Conversion Factors
\newblock{\em Proc. J. Kor. Nucl. Soc. 1980}, pp171-179
